Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-24 presentation/presentation.tex
Final Version 2

	\item {
	Does idiosyncratic risk matter? How do changes in such risk affect other economic variables? Are there distributional consequences?
	}

@@

\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution1}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution2}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution3}
  \end{minipage}
\end{figure}
\ \ \ \ \ \ \  rw = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.8
\end{frame}

@@

	\item {
Idiosyncratic risk matters: 
Precautionary savings increase with higher uncertainty, thus increasing aggregate capital. 
	}	
	\item {
Increasing unemployment benefits has distributional consequences. 
	}

>>>>

	\item {
How do changes in idisynratic risk affect other economic variables in the long run? How do these results compare to an economy with perfect markets? Are there distributional consequences?
	}

@@

\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution1}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution2}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.325\textwidth}
    \includegraphics[width=\textwidth]{distribution3}
  \end{minipage}
\end{figure}
\ \ \ \ \ \ \  UI = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.8
\end{frame}

@@

	\item {
The presence of idiosyncratic risk leads to higher aggregate capital. 
	}
		\item {
A model with idiosyncratic risk allows for the study of distributional questions.
	}	
	\item {
Increasing unemployment benefits has distributional consequences. 
	}
